Trajectories

### 2023-02-02 docs/index.qmd
Documents functions

The 95% *HDI* of the regression coefficient of the **number of phonemes** did exclude the *ROPE*, although not by much: `r percent(post_draws_list[["b_n_phon_std"]]$rope_percentage, accuracy = 0.01)` of its posterior samples fell within the *ROPE*. This suggests that the number of phonemes in the word form had a small effect on the probability of acquisition ($\beta$ = `r percent(post_draws_list[["b_n_phon_std"]]$.median, accuracy = 0.01)`, 95% *HDI* = [`r percent(post_draws_list[["b_n_phon_std"]]$.lower, accuracy = 0.01)`, `r percent(post_draws_list[["b_n_phon_std"]]$.upper, accuracy = 0.01)`]). For every increase in phoneme length, the probability of acquisition decreased in `r percent(post_draws_list[["b_n_phon_std"]]$.median/(4*sd(responses$n_phon)), accuracy = 0.01)`.

**Exposure** ($Exposure$) had a strong effect on the probability of acquisition ($\beta$ = `r percent(post_draws_list[["b_exposure_std"]]$.median, accuracy = 0.01)`, 95% *HDI* = [`r percent(post_draws_list[["b_exposure_std"]]$.lower, accuracy = 0.01)`, `r percent(post_draws_list[["b_exposure_std"]]$.upper, accuracy = 0.01)`]). All of the posterior samples of his regression excluded the *ROPE*. The impact of this predictor on the probability of acquisition was positive: for every SD increase in exposure rate, the participant was `r percent(post_draws_list[["b_exposure_std"]]$.median/(sd(responses$b_exposure_std)), accuracy = 0.01)` more likely to acquire it.

The effect of **phonological similarity** by itself (as indicated by the regression coefficient of the main effect of $Levenshtein$) was equivalent to zero ($\beta$ = `r percent(post_draws_list[["b_lv_std"]]$.median, accuracy = 0.01)`, 95% *HDI* = [`r percent(post_draws_list[["b_lv_std"]]$.lower, accuracy = 0.01)`, `r percent(post_draws_list[["b_lv_std"]]$.upper, accuracy = 0.01)`]), as `r percent(post_draws_list[["b_lv_std"]]$rope_percentage, accuracy = 0.01)` of the posterior samples of its regression coefficient fell into the *ROPE*.

@@

The 95% *HDI* of the regression coefficient of the $Age \times Exposure$ interaction did not exclude the *ROPE* ($\beta$ = `r percent(post_draws_list[["b_age_std:exposure_std"]]$.median, accuracy = 0.01)`, 95% *HDI* = [`r percent(post_draws_list[["b_age_std:exposure_std"]]$.lower, accuracy = 0.01)`, `r percent(post_draws_list[["b_age_std:exposure_std"]]$.upper, accuracy = 0.01)`]): `r percent(post_draws_list[["b_age_std:exposure_std"]]$rope_percentage, accuracy = 0.01)` of its posterior samples fell within the *ROPE*. This shows that the effect of exposure on the speed at which participants acquired words across ages was inconclusive. Given our data, it is difficult to tell whether this *Exposure* increased or decreased the slope of the words' acquisition trajectories.

@@

## Marginal predictions

>>>>

The 95% *HDI* of the regression coefficient of the **number of phonemes** did exclude the *ROPE*, although not by much: `r percent(post_draws_list[["b_n_phon_std"]]$.rope_overlap, accuracy = 0.01)` of its posterior samples fell within the *ROPE*. This suggests that the number of phonemes in the word form had a small effect on the probability of acquisition ($\beta$ = `r percent(post_draws_list[["b_n_phon_std"]]$.median, accuracy = 0.01)`, 95% *HDI* = [`r percent(post_draws_list[["b_n_phon_std"]]$.lower, accuracy = 0.01)`, `r percent(post_draws_list[["b_n_phon_std"]]$.upper, accuracy = 0.01)`]). For every increase in phoneme length, the probability of acquisition decreased in `r percent(post_draws_list[["b_n_phon_std"]]$.median/(4*sd(responses$n_phon)), accuracy = 0.01)`.

**Exposure** ($Exposure$) had a strong effect on the probability of acquisition ($\beta$ = `r percent(post_draws_list[["b_exposure_std"]]$.median, accuracy = 0.01)`, 95% *HDI* = [`r percent(post_draws_list[["b_exposure_std"]]$.lower, accuracy = 0.01)`, `r percent(post_draws_list[["b_exposure_std"]]$.upper, accuracy = 0.01)`]). All of the posterior samples of his regression excluded the *ROPE*. The impact of this predictor on the probability of acquisition was positive: for every SD increase in exposure rate, the participant was `r percent(post_draws_list[["b_exposure_std"]]$.median/(4*sd(responses$exposure)), accuracy = 0.01)` more likely to acquire it.

The effect of **phonological similarity** by itself (as indicated by the regression coefficient of the main effect of $Levenshtein$) was equivalent to zero ($\beta$ = `r percent(post_draws_list[["b_lv_std"]]$.median, accuracy = 0.01)`, 95% *HDI* = [`r percent(post_draws_list[["b_lv_std"]]$.lower, accuracy = 0.01)`, `r percent(post_draws_list[["b_lv_std"]]$.upper, accuracy = 0.01)`]), as `r percent(post_draws_list[["b_lv_std"]]$.rope_overlap, accuracy = 0.01)` of the posterior samples of its regression coefficient fell into the *ROPE*.

@@

The 95% *HDI* of the regression coefficient of the $Age \times Exposure$ interaction did not exclude the *ROPE* ($\beta$ = `r percent(post_draws_list[["b_age_std:exposure_std"]]$.median, accuracy = 0.01)`, 95% *HDI* = [`r percent(post_draws_list[["b_age_std:exposure_std"]]$.lower, accuracy = 0.01)`, `r percent(post_draws_list[["b_age_std:exposure_std"]]$.upper, accuracy = 0.01)`]): `r percent(post_draws_list[["b_age_std:exposure_std"]]$.rope_overlap, accuracy = 0.01)` of its posterior samples fell within the *ROPE*. This shows that the effect of exposure on the speed at which participants acquired words across ages was inconclusive. Given our data, it is difficult to tell whether this *Exposure* increased or decreased the slope of the words' acquisition trajectories.

@@
